### 2017-05-06 paper/evaluation.tex
pass on rq6

To answer this research question, we conducted an experiment involving
the six parallel configurations from Section~\ref{sec:modes}  and the
top 10 long-running test modules from our sample
set. The rationale for this selection criteria was to maximize the
chances of observing speedup and flakiness, assuming that long-running
tests also have many tests. Indeed, we confirmed that test suites in
these projects contain at least \Fix{X} tests. Also, we preferred to
compare the effect of a configuration over a single test module for
projects with multiple test modules.  Recall that large projects may
contain several test modules, and these modules may contain distinct
characteristics that could favor one configuration and not others;
therefore, it would be necessary to check each module individually for
a fair comparison.  We are interested in understanding how efficiency
(\ie, testing cost) and flakiness (\ie, failing tests) are affected
when we run a test suite with different parallel configurations.
Recall that increased resource contention obtained with parallelism
can lead to concurrency issues such as data races.  Flakiness and
speedup are contradictory forces that drive configuration selection.
We used as a \emph{control group} (\ie, baseline) the sequential
execution of each subject's tests. Notice that for measuring
flakiness, we have to consider only tests that failed due to the
concurrency in the parallel execution.  For that reason, we
re-executed the tests in sequence ten times and carefully verified
that there are only passing tests in our baseline.  We considered ten
as the number of re-executions based on the approach used by Google
reported in a previous work on test flakiness~\cite{luo-etal-fse2014}.
To obtain parallel configurations, we implemented a script that takes
a subject and a configuration (\eg, \ForkSeq{}) as inputs, and the
script outputs the modified version of the subject with the desired
configuration. The workflow consists in copying the project directory
to a new directory, finding all existing build files (\ie, \pomf{}
files), and modifying all existing Maven Surefire configurations with
new values for the parameters \CodeIn{parallel}, \CodeIn{forkCount},
and \CodeIn{threadCount} using an XPath~\cite{xpath} library to
manipulate XML documents. For configurations with forked JVMs enabled
(\ie, \ForkSeq{} and \ForkParMeth{}), we changed the
\CodeIn{forkCount} with the value \CodeIn{1C} (\ie, one JVM per core).
To adjust the pool of threads for parallelism within a JVM, we changed
the parameter \CodeIn{threadCount} with \Jbc{should we consider 2 as
it is the number of native threads per core OR 6 as it represents 3
Cores * 2 native threads?}.  To run the subjects and their respective
variations (\ie, the modified versions according to the parallelism
configuration), we used a similar approach as described in
Figure~\ref{fig:mvn-execution} except that we added a timeout of one
hour to run the tests. We used the \CodeIn{timeout}
command~\cite{timeout-cmd} to monitor the execution, and we configured
the command to dispatch a \emph{kill} signal if the test execution
exceeds the time limit. We imposed this time constraint to avoid
hanging indefinitely the experiment execution due to some thread
contention that may occur (\eg, deadlock). Finally, we saved each
execution log and XML test reports generated by Maven to collect the
execution time, the number of failing tests, and for reference to
analyze and diagnose outliers in our results. For efficiency, we
reported the speedup (\ie, $\Uparrow_\text{speed} = T_{\text{s}} /
T_{\text{p}}$) in average, and for flakiness, we reported the rate of
failing tests (\ie, $\mathit{\%_\text{fail} = failures / tests}$) in
average.  Figure~\ref{tab:rq6-table} summarizes the obtained results
ordered by the time cost (\ie, $T_\text{cost}$).

>>>>

To answer this research question, we conducted an experiment involving
the six parallel configurations from Section~\ref{sec:modes}  and the
top 10 long-running test modules from our sample set. The rationale
for this selection criteria was to maximize the chances of observing
speedup and flakiness, assuming that long-running tests also have many
tests. Indeed, we confirmed that test suites in these projects contain
at least 236 tests ($1,662.7$ in average). Also, we preferred to compare the
effect of a configuration over a single test module for projects with
multiple test modules.  Recall that large projects may contain several
test modules, and these modules may contain distinct characteristics
that could favor one configuration and not others; therefore, it would
be necessary to check each module individually for a fair comparison.
We are interested in understanding how efficiency (\ie, testing cost)
and flakiness (\ie, failing tests) are affected when we run a test
suite with different parallel configurations.  Recall that increased
resource contention obtained with parallelism can lead to concurrency
issues such as data races.  Flakiness and speedup are contradictory
forces that drive configuration selection.  We used as a \emph{control
group} (\ie, baseline) the sequential execution of each subject's
tests. Notice that for measuring flakiness, we have to consider only
tests that failed due to the concurrency in the parallel execution.
For that reason, we re-executed the tests in sequence ten times and
carefully verified that there are only passing tests in our baseline.
We considered ten as the number of re-executions based on the approach
used by Google reported in a previous work on test
flakiness~\cite{luo-etal-fse2014}.  To obtain parallel configurations,
we implemented a script that takes a subject and a configuration (\eg,
\ForkSeq{}) as inputs, and the script outputs the modified version of
the subject with the desired configuration. The workflow consists in
copying the project directory to a new directory, finding all existing
build files (\ie, \pomf{} files), and modifying all existing Maven
Surefire configurations with new values for the parameters
\CodeIn{parallel}, \CodeIn{forkCount}, and \CodeIn{threadCount} using
an XPath~\cite{xpath} library to manipulate XML documents. For
configurations with forked JVMs enabled (\ie, \ForkSeq{} and
\ForkParMeth{}), we changed the \CodeIn{forkCount} with the value
\CodeIn{1C} (\ie, one JVM per core).  To adjust the pool of threads
for parallelism within a JVM, we changed the parameter
\CodeIn{threadCount} with \Jbc{should we consider 2 as it is the
number of native threads per core OR 6 as it represents 3 Cores * 2
native threads?}.  To run the subjects and their respective variations
(\ie, the modified versions according to the parallelism
configuration), we used a similar approach as described in
Figure~\ref{fig:mvn-execution} except that we added a timeout of one
hour to run the tests. We used the \CodeIn{timeout}
command~\cite{timeout-cmd} to monitor the execution, and we configured
the command to dispatch a \emph{kill} signal if the test execution
exceeds the time limit. We imposed this time constraint to avoid
hanging indefinitely the experiment execution due to some thread
contention that may occur (\eg, deadlock). Finally, we saved each
execution log and XML test reports generated by Maven to collect the
execution time, the number of failing tests, and for reference to
analyze and diagnose outliers in our results. For efficiency, we
reported the speedup (\ie, $\Uparrow_\text{speed} = T_{\text{s}} /
T_{\text{p}}$) in average, and for flakiness, we reported the rate of
failing tests (\ie, $\mathit{\%_\text{fail} = failures / tests}$) in
average.  Figure~\ref{tab:rq6-table} summarizes the obtained results
ordered by the time cost (\ie, $T_\text{cost}$). \Fix{Remember to
explain efficiency cutoff, JVM crashes and timeout}
